\chapter{Introduction} \label{chap_introduction}

\section{Motivation}

The final thesis is an integral part of international students' study at Lübeck University of Applied Sciences (THL). Although final-year students have already spent several years studying in English before working on their theses, many of them do not know how to write such a specific-purposed document. Admittedly, there are many thesis guidelines and related literature available (e.g. \cite{les06}), but each university has its own rules and requirements for writing a thesis. Therefore, it is highly desirable that a thesis guideline/template be provided specially for the international students at THL.

The authors of this document in chronological order are Horst Hellbrück, Zhi Haolin, Aida Bahta, Ren Zhong and Andreas Hanemann. Horst Hellbrück has started the document and the structure in 2009 with Zhi Haolin providing most of the texts in the first version. Ren Zhong has rewritten and rephrased most of the texts and extended the documentation in 2012 resulting in this comprehensive guideline. Further additions have been made by Andreas Hanemann in early 2013 using input from Aida Bahta and further THL instruction documents. Andreas Hanemann has also converted the Word template into this LaTeX template.

Important: This document is not a legal basis. Refer to the examination regulations. The instructions of the supervisor are authoritative for the student's thesis.

\section{Goal}

This document is intended to assist the final-year students in the international study programs at THL to write their theses. The goal of the document is twofold. On one hand, it serves as a guideline for the students looking for practical help, including structure, language, writing strategies, format, etc. On the other hand, this document is also a template of a thesis created with LaTeX (more precisely MikTeX in combination with TeXstudio under Microsoft Windows; Biber is used instead of Bibtex). It strictly follows the formatting requirements for a thesis at THL. Students are encouraged to replace the text with their own content and use this template as a starting point of their theses.

\section{Organization}

The rest of the document is structured as follows. Chapter \ref{chap_process} explains the procedure for writing a thesis at THL. It comprises the colloquium as well. Chapter \ref{chap_structure} explains the typical structure for a thesis and provides a typical example. Chapter \ref{chap_writing} discusses the use of language in a thesis and specifies the formatting requirements. Chapter \ref{chap_summary} summarizes the work, and suggests future work that could be done to improve this document. In the Appendix a list of frequently asked questions covers many questions often asked by students.

\endinput
