\chapter{Acknowledgements} \label{chap_acknowledgements}

This section contains acknowledgements from the main authors of this document.

\paragraph{Acknowledgments by Horst Hellbrück}

I want to thank all staff members and students that have participated in this document by giving tips or by asking questions. When I have started this guide in 2009 with a vague idea in mind, I could not foresee that this document becomes such a great help for all the students. My special thanks go to Zhi Haolin and Ren Zhong from the international study program Information Technology at Lübeck University of Applied Sciences together with ECUST in Shanghai. They have written most of the texts and provided references and figures. Without their valuable contribution this guide would have stayed at a conceptual level.

\paragraph{Acknowledgements by Ren Zhong}

I would like to express my gratitude to Prof. Dr.-Ing Horst Hellbrück, who wrote the first draft of this document, and offered me such a great opportunity to contribute to this meaningful work.

\paragraph{Acknowledgements by Andreas Hanemann}

I would like to thank the people who have worked on this document earlier (Horst Hellbrück, Zhi Haolin, Aida Bahta, Ren Zhong). Some advice from Hermann Hochhaus and Hans-Günter Kunze has also been included into the document.

Recommendations by Marco Trettner for additional packages and commands have been included in the beginning of the document.

\paragraph{} The authors hope that students can benefit from the document and that more students may add contributions to this document to improve it.


\endinput 